Spfy: bringing real-time, big data batch analyses of E. coli to SuperPhy

### 2017-12-21 paper-proposal.tex
ADD: NAR layout + citations

\documentclass{article}
\usepackage[parfill]{parskip}
\usepackage[backend=bibtex,style=numeric-comp]{biblatex}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
\bibliography{paper-webserver.bib}

\begin{document}
% "contain, at the top, the following affirmative statement. "This website is free and open to all users and there is no login requirement." Additionally, any third party software employed by the website that has more restrictive usage terms must be listed."
This website is free and open to all users and there is no login requirement. The code for this webserver, and all third party software used, are available under the open-source Apache 2.0, BSD 3-clause, or similar licenses. \par

@@

% "and two to four keywords."
Keywords: Bioinformatics, Graph database, Real-time analysis
\end{document}

>>>>

\documentclass[a4,center,fleqn]{NAR}
\RequirePackage{hyperref}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage[parfill]{parskip}
% \usepackage[backend=bibtex,style=numeric-comp]{biblatex}
% \usepackage[letterpaper, portrait, margin=1in]{geometry}

\begin{document}

\title{Spfy: bringing real-time, big data batch analyses of E. coli to SuperPhy}

\author{%
Kevin K Le\,$^{1,*}$,
Matthew D Whiteside\,$^{1}$,
Chad R Laing\,$^1$,
and Victor PJ Gannon\,$^1$%
\footnote{To whom correspondence should be addressed.
Tel: +1 403-382-5516; Fax: +1 403-381-1202; Email: chad.r.laing@phac-aspc.gc.ca}}

\address{%
$^{1}$Laboratory for Foodborne Zoonoses, Public Health Agency of Canada, Twp Rd 9-1, Lethbridge, AB, T1J 3Z4, Canada}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

\maketitle

% "contain, at the top, the following affirmative statement. "This website is free and open to all users and there is no login requirement." Additionally, any third party software employed by the website that has more restrictive usage terms must be listed."
This website is free and open to all users and there is no login requirement. The code for this webserver, and all third party software used, are available under the open-source Apache 2.0, BSD 3-clause, or similar licenses. \par

@@

% "and two to four keywords."
Keywords: Comparative genomics analysis, Epidemiology, Microbial genomics

\newpage

\begin{thebibliography}{4}

\bibitem{whiteside2016superphy}
Whiteside, M.D., Laing, C.R., Manji, A., Kruczkiewicz, P., Taboada, E.N., and Gannon, V.P.J. (2016)
SuperPhy: predictive genomics for the bacterial pathogen Escherichia coli.
\textit{BMC Microbiol}, \textbf{16}, 65.

\bibitem{goecks2010galaxy}
Goecks, J., Nekrutenko, A., Taylor, J. (2010)
Galaxy: a comprehensive approach for supporting accessible, reproducible, and transparent computational research in the life sciences.
\textit{Genome Biol}, \textbf{11}, R86.

\bibitem{thomsen2016bacterial}
Thomsen, M.C.F., Ahrenfeldt, J., Cisneros, J.L.B., Jurtz, V., Larsen, M.V., Hasman, H., Aarestrup, F.M., and Lund, O. (2016)
A bacterial analysis platform: an integrated system for analysing bacterial whole genome sequencing data for clinical diagnostics and surveillance.
\textit{PloS One}, \textbf{11}, e0157718.

\bibitem{griffiths2017context}
Griffiths, E., Dooley, D., Graham, M., Van Domselaar, G., Brinkman, F.S.L., and Hsiao, W.W.L. (2017)
Context Is Everything: Harmonization of Critical Food Microbiology Descriptors and Metadata for Improved Food Safety and Surveillance
\textit{Front Microbiol}, \textbf{8}, 1068.

\bibitem{bolleman2016faldo}
Bolleman, J.T., Mungall, C.J., Strozzi, F., Baran, J., Dumontier, M., Bonnal, R.J.P., Buels, R., Hoehndorf, R., Fujisawa, T., Katayama, T., et al. (2016)
FALDO: a semantic standard for describing the location of nucleotide and protein feature annotation.
\textit{BMC J Biomed Sem}, \textbf{7}, 1068.

\bibitem{vaz2014typon}
Vaz, C., Francisco, A.P., Silva, M., Jolley, K.A., Bray, J.E., Puseele, H., Rothganger, J., Ramirez, M., Carri\c{c}o, J.A. (2014)
TypOn: the microbial typing ontology
\textit{BMC J Biomed Sem}, \textbf{5}, 43.

\end{thebibliography}

\end{document}
